### 2021-04-21 README.rmd
updating the README

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  fig.path = "man/figures/",
  out.width = "100%"
)
```

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  fig.path = "man/figures/",
  out.width = "100%"
)
library(badger)
```
